Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-10 paper/paper.tex
polishing prioritization

Figure~\ref{fig:workflow} illustrates the infrastructure for
differential testing, which is used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Note that a number of reasons exist, other than a bug, to
explain discrepancy (see Table~\ref{tab:false-positives}). We used the
open-source eshost-cli project~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distinguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups.

@@

Considering prioritization, we classified warnings in two kinds,
reflecting their likelihood to manifest a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifests discrepancy through violation of an assertion
declared in the test. In contrast, warnings in the ``\lo{}'' group are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions
not related to the test itself. We found that different engines often
check pre-conditions of those functions differently. It can happen,
for example, that one engine enforces a weaker pre-condition on a
function input compared to another engine and that is acceptable. In
those cases, the infrastructure would observe a discrepancy that is
more likely to be associated with an invalid input produced by the
fuzzer, \ie{}, it is likely to be a bug in the test code not the
engine (library or runtime) code. Although we did find real bugs from
``\lo{}'' warnings, the proportion was much lower compared to
``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
found with fuzzing originated from ``\lo{}'' warnings. \Fix{quickly
  explain why LO can still be a bug.}

>>>>

Figure~\ref{fig:workflow} illustrates the infrastructure for
differential testing, which is used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. The infrastructure uses the
open-source tool eshost-cli~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

Note that a number of reasons exist, other than a bug, to explain
discrepancy (see Table~\ref{tab:false-positives}) and there is no
clear way to distinguish false and true positives automatically. As
such, a human needs to inspect the warning to classify the issue. To
facilitate inspection, we prioritized warnings and clustered them in
groups. We describe these strategies in the following.

@@

Considering prioritization, we classified warnings in two kinds,
reflecting their likelihood of manifesting a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks, but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifests discrepancy through violation of an assertion
declared in the test. In contrast, warnings in the ``\lo{}'' group are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions,
which are part of the application. We found that different engines often
check pre-conditions of those functions differently. It can happen,
for example, that one engine enforces a weaker pre-condition on a
function input compared to another engine and that is acceptable. For
instance, it is acceptable to pass values greater than \Fix{x} to
function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}. In
those cases, the infrastructure would observe a discrepancy that is
more likely to be associated with an invalid input produced by the
fuzzer, \ie{}, it is likely to be a bug in the test code not the
engine (library or runtime) code. Although we did find real bugs from
``\lo{}'' warnings, the proportion was much lower compared to
``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
found with fuzzing originated from ``\lo{}'' warnings. \Fix{quickly
  explain why LO can still be a bug.}
